A numerical study of fixation probabilities for strategies in the Iterated Prisoner's Dilemma

### 2017-04-15 tex/main.tex
Add acknowledgements of Raven.
Add some early analysis of rank vs N.

% Packages
\usepackage[margin=1.5cm, includefoot, footskip=30pt]{geometry}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{xstring}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{standalone}

@@

All strategies are paired and these pairs are used in 1000 repetitions of a
Moran process assuming a starting population of \((N/2, N/2)\). This is repeated
for even \(N\) between 2 and 14. The fixation probability is then estimated for
each value of \(N\).

@@

% TODO Discuss effect of size on performance of strategies. Relate to Press and
% Dyson work: "ZD strategies win matches but not tournaments".

@@

% TODO Include discussion about noise.

@@

>>>>

% Packages
\usepackage[margin=1.5cm, includefoot, footskip=30pt]{geometry}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{xstring}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{standalone}
\usepackage{fancyvrb}

@@

All strategies are paired and these pairs are used in 2000 repetitions of a
Moran process assuming a starting population of \((N/2, N/2)\). This is repeated
for even \(N\) between 2 and 14. The fixation probability is then estimated for
each value of \(N\).

@@

Figures~\ref{fig:ranks_v_size_standard} and~\ref{fig:ranks_v_size_noisy} show
the median rank of each strategy against population size in the standard and
noisy settings. Note that these ranks are not necessarily integers as group ties
are given the average rank.

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{../img/median_rank_vs_population_size_std.pdf}
    \caption{Median (inverse) rank of players against population size}
    \label{fig:ranks_v_size_standard}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{../img/median_rank_vs_population_size_noisy.pdf}
    \caption{Median (inverse) rank of players against population size with noise}
    \label{fig:ranks_v_size_noisy}
\end{figure}

Tables~\ref{tbl:ranks_in_size_2_std},~\ref{tbl:ranks_in_size_14_std},~\ref{tbl:ranks_in_size_2_noisy}
and~\ref{tbl:ranks_in_size_14_noisy} show the rankings across population size
based for the top on bottom performers across the extreme population sizes.

\begin{table}[!hbtp]
    \centering
        \begin{subfigure}[t]{\textwidth}
            \centering
                \input{../tbl/top_five_in_size_2_std.tex}
            \label{tbl:top_five_in_size_2_std}
        \end{subfigure}

        \begin{subfigure}[t]{\textwidth}
            \centering
                \input{../tbl/bottom_five_in_size_2_std.tex}
            \label{tbl:bottom_five_in_size_2_std}
        \end{subfigure}%
        \caption{Performance across population sizes of top and bottom
        performing strategies in population size \(N=2\)}
        \label{tbl:ranks_in_size_2_std}
\end{table}

\begin{table}[!hbtp]
    \centering
        \begin{subfigure}[t]{\textwidth}
            \centering
                \input{../tbl/top_five_in_size_14_std.tex}
            \label{tbl:top_five_in_size_14_std}
        \end{subfigure}

        \begin{subfigure}[t]{\textwidth}
            \centering
                \input{../tbl/bottom_five_in_size_14_std.tex}
            \label{tbl:bottom_five_in_size_14_std}
        \end{subfigure}%
        \caption{Performance across population sizes of top and bottom
        performing strategies in population size \(N=14\)}
        \label{tbl:ranks_in_size_14_std}
\end{table}

\begin{table}[!hbtp]
    \centering
        \begin{subfigure}[t]{\textwidth}
            \centering
                \input{../tbl/top_five_in_size_2_noisy.tex}
            \label{tbl:top_five_in_size_2_noisy}
        \end{subfigure}

        \begin{subfigure}[t]{\textwidth}
            \centering
                \input{../tbl/bottom_five_in_size_2_noisy.tex}
            \label{tbl:bottom_five_in_size_2_noisy}
        \end{subfigure}%
        \caption{Performance across population sizes of top and bottom
        performing strategies in population size \(N=2\) (with noise)}
        \label{tbl:ranks_in_size_2_noisy}
\end{table}

\begin{table}[!hbtp]
    \centering
        \begin{subfigure}[t]{\textwidth}
            \centering
                \input{../tbl/top_five_in_size_14_noisy.tex}
            \label{tbl:top_five_in_size_14_noisy}
        \end{subfigure}

        \begin{subfigure}[t]{\textwidth}
            \centering
                \input{../tbl/bottom_five_in_size_14_noisy.tex}
            \label{tbl:bottom_five_in_size_14_noisy}
        \end{subfigure}%
        \caption{Performance across population sizes of top and bottom
        performing strategies in population size \(N=14\) (with noise)}
        \label{tbl:ranks_in_size_14_noisy}
\end{table}

Table~\ref{tbl:median_rank_v_memory_length} shows the performance based on
memory length.

\begin{table}[!hbtp]
    \centering
        \begin{subfigure}[t]{\textwidth}
            \centering
                \input{../tbl/median_rank_v_memory_length_std.tex}
            \caption{Standard}
            \label{tbl:top_five_in_size_14_noisy}
        \end{subfigure}

        \begin{subfigure}[t]{\textwidth}
            \centering
                \input{../tbl/median_rank_v_memory_length_noisy.tex}
            \caption{Noisy}
            \label{tbl:bottom_five_in_size_14_noisy}
        \end{subfigure}%
        \caption{Median rank by memory length}
        \label{tbl:median_rank_v_memory_length}
\end{table}

% TODO Discuss effect of size on performance of strategies. Relate to Press and
% Dyson work: "ZD strategies win matches but not tournaments".
% TODO Include discussion about noise.

@@

@@

\section*{Acknowledgements}

This work was performed using the computational facilities of the Advanced
Research Computing @ Cardiff (ARCCA) Division, Cardiff University.
